---
title: "Group Project"
author: "DataChefs"
date: "12/12/2017"
output: html_document
runtime: shiny
---

```{r setup, include=T}
knitr::opts_chunk$set(echo = T)
```
### test result


### create Data Table for Hourly Measurments from ####

In this block we create a list of all the csv files in the data folder.
Then we create of all the files rbind together while creating a column for each list extracted from the date in the csv name.
Then last step we split the year and the month

```{r raw_data_reading, echo=T}
library(data.table)
library(knitr)
setwd("C:/Term_1/R_programing/project")
filenames <- list.files("workgroup_data", pattern="*.csv", full.names=TRUE)
ldf<-do.call(rbind, lapply(filenames, function(x) cbind(fread(x), Year=strsplit(regmatches(x, regexpr("*[0-9].[_][0-9]*", x)),split="_")[[1]][1],Month=strsplit(regmatches(x, regexpr("*[0-9].[_][0-9]*", x)),split="_")[[1]][2])))
PTable <- data.table(ldf)
PTable$parameter<-as.factor(PTable$parameter)
str(PTable)
```
### Read Weather data from Excel
```{r Read_Weather_data, echo=T}
library(readxl) 
weather_data<-data.table(read_excel('weather.xlsx'))
str(weather_data)
```
### Create Data table for Polutants Types
```{r create_table _pollutants, echo=T}
PID<-c(01,06,07,08,09,10,12,14,20,30,35,37,38,39,42,43,44)
PID
PName<-c('SO2','CO','NO','NO2','PM2.5','PM10','NOx','O3','TOL','BEN','EBE','MXY','PXY','OXY','TCH','CH4','NMHC')
pollutants<-data.table(cbind(PID,PName))
str(pollutants)

```


### Get Daily Record from Hourly Pollutant Data
Aggregate the mean of the measure value by day, month, year and pollutant

```{r raw_data_get_daily, echo=T}
Daily_Pollution_Data_by_Par<-PTable[ ,list(Value=mean(value, na.rm = T)),by=list(Month,Year,day,parameter)]
str(Daily_Pollution_Data_by_Par)
```
### Merge Pollutants Names with Daily Pollutants Events
```{r Merge_Pollutants_Daily_Values, echo=T}
Daily_Pollution_Data_by_Par$parameter<-as.factor(Daily_Pollution_Data_by_Par$parameter)
pollutants$PID<-as.factor(pollutants$PID)
setkey(Daily_Pollution_Data_by_Par,parameter)
setkey(pollutants,PID)
Daily_Pollutants_Values<-pollutants[Daily_Pollution_Data_by_Par, nomatch=0]
str(Daily_Pollutants_Values)
```
### Merging Pollutant daily values with daily weather data and create final dataset for Analysis
```{r Merging_Weather_and _Pollutants, echo=T}
library (dplyr)
Daily_Pollutants_Values$Twenty<-rep(20, nrow(Daily_Pollutants_Values))
Daily_Pollutants_Values$Time<-rep("000000",nrow(Daily_Pollutants_Values))
Daily_Pollutants_Values$Year<- with(Daily_Pollutants_Values, paste0(Twenty,Year))
Daily_Pollutants_Values$date <- as.character(with(Daily_Pollutants_Values, paste(Year, Month, day,sep="-")), "%Y-%m-%d")
Daily_Pollutants_Values$date<- as.POSIXct(paste(Daily_Pollutants_Values$date, Daily_Pollutants_Values$Time), format="%Y-%m-%d %H%M%S",tz = "UTC")
Daily_Pollutants_Values$Twenty<-NULL
Daily_Pollutants_Values$Time<-NULL
str(Daily_Pollutants_Values)
attr(weather_data$date, "tzone")
attr(Daily_Pollutants_Values$date, "tzone")
str(weather_data)
setkey(Daily_Pollutants_Values,date)
setkey(weather_data,date)
DWPD<-data.table(Daily_Pollutants_Values[weather_data, nomatch=0])
str(DWPD)
DWPD<-DWPD[PName %in% c('NO2','SO2','O3','PM2.5') , .(PID,PName,Month,Year,day,Value,date,temp_avg,temp_max,temp_min,precipitation,humidity,wind_avg_speed)]
#DWPD<-DWPD [, list(Value := round(Value,4)),by(PID,PName,Month,Year,day,Value,date,temp_avg,temp_max,temp_min,precipitation,humidity,wind_avg_speed)]
DWPD[1:10,]
DWPD_wide<-dcast(DWPD, date + temp_avg +humidity+ wind_avg_speed+precipitation ~ PName,value.var = 'Value')
str(DWPD_wide)
```

### Time series graphs with Loop
```{r Time Series Graph Loop, echo=T}
library(dygraphs)
library(xts)
TimeSeriesGraphs<-function(x)
{
  DWPD_wide_ts<-xts(x, order.by=x$date)
myDyGraph <- dygraph(DWPD_wide_ts)
str(DWPD_wide_ts)
result <- lapply(1:length(DWPD_wide_ts), function(i) if (names(DWPD_wide_ts)[i]%in% c('cno2_ma','SO2','O3','PM2.5')) {dygraph(DWPD_wide_ts[,i], main = c(names(DWPD_wide_ts)[i]," Time Series"))%>%  dyRangeSelector() %>% dyOptions(colors = RColorBrewer::brewer.pal(3, "Set2")) 
})
return (result)
}
res<-TimeSeriesGraphs(DWPD_wide)
res<-res[-which(sapply(res, is.null))]
htmltools::tagList(res)


```

## Relations between Pollutants and weather data

```{r echo=FALSE}
library(ggplot2)
library(plotly)
library(magrittr)
library(ggpubr)
library(gridExtra)
library(cowplot)
require(ggplot2)
shinyApp(
  ui = fluidPage(
    selectInput("Pollutant", label = "Select Pollutant",
              choices = c('NO2'='NO2',"SO2"="SO2", "O3"="O3","PM2.5"="PM2.5" ), selected ='NO2' ),
    selectInput("weatherVar", label = "Select Weather Variable",
              choices = c("temp_avg"='temp_avg',"humidity"="humidity", "wind_avg_speed"="wind_avg_speed","precipitation"="precipitation" ), selected ='temp_avg' ),
    plotOutput("cityplt")
  ),
  server = function(input, output) {
  
   # if(input$Pollutant=='NO2' & input$weatherVar=='temp_avg')
    #{
     # xaxis<-'NO2'
      #yaxis<-'tem_avg'
    #}
    output$cityplt <- renderPlot({
      ggplot(DWPD_wide, aes(x=DWPD_wide[[input$Pollutant]],y=DWPD_wide[[input$weatherVar]])) + geom_point(size=2.5)+
    stat_smooth(method='auto')+
  labs(x=input$Pollutant,y=input$weatherVar)
    })
  },
  options = list(height = 800)

)





```


### Corrolation Matrix
```{r corrolation matrix, echo=T }
library(corrplot)
str(DWPD_wide)
data_sample<-DWPD_wide[,.(NO2,SO2,O3,PM2.5)]
head(data_sample)
corrplot(cor(data_sample), method = 'number', tl.col = 'black')

library(GGally)

p<-GGally::ggpairs(data_sample,axisLabels = 'none',size=1,lwd=0.5,alpha=.5)

ggplotly(p, width = 800, height = 500)
```


###Further Analysis
```{r, echo=T}
library(forecast)
library(tseries)
library(fpp)
DWPD_wide$date2<-as.Date(DWPD_wide$date)
ggplot(DWPD_wide, aes(date2, NO2)) + geom_line() + scale_x_date('month')  + ylab("NO2") +
            xlab("")
count_ts = ts(DWPD_wide[, c('NO2')])

DWPD_wide$clean_NO2 = tsclean(count_ts)

ggplot() +
  geom_line(data = DWPD_wide, aes(x = date2, y = clean_NO2)) + ylab('Clean No2 Count')

DWPD_wide$cnt_ma = ma(DWPD_wide$clean_NO2, order=7) # using the clean count with no outliers
DWPD_wide$cnt_ma30 = ma(DWPD_wide$clean_NO2, order=30)

ggplot() +
  geom_line(data = DWPD_wide, aes(x = date2, y = clean_NO2, colour = "Counts")) +
  geom_line(data = DWPD_wide, aes(x = date2, y = cnt_ma,   colour = "Weekly Moving Average"))  +
  geom_line(data = DWPD_wide, aes(x = date2, y = cnt_ma30, colour = "Monthly Moving Average"))  +
  ylab('No2 Count')

ggplot() +
  geom_line(data = DWPD_wide, aes(x = date2, y = cnt_ma,   colour = "Weekly Moving Average"))  +
  ylab('No2 Count')

ggplot() +
  geom_line(data = DWPD_wide, aes(x = date2, y = cnt_ma30, colour = "Monthly Moving Average"))  +
  ylab('No2 Count')

allow.multiplicative.trend=TRUE 

count_ma = ts(na.omit(DWPD_wide$cnt_ma), frequency=30)
decomp = stl(count_ma, s.window="periodic")
deseasonal_cnt <- seasadj(decomp)
plot(decomp)

Acf(count_ma, main='')

Pacf(count_ma, main='')

count_d1 = diff(deseasonal_cnt, differences = 1)
plot(count_d1)
adf.test(count_d1, alternative = "stationary")

Acf(count_d1, main='ACF for Differenced Series')
Pacf(count_d1, main='PACF for Differenced Series')

auto.arima(deseasonal_cnt, seasonal=FALSE)

fit<-auto.arima(deseasonal_cnt, seasonal=FALSE)
tsdisplay(residuals(fit), lag.max=45, main='(1,1,1) Model Residuals')

fit2 = arima(deseasonal_cnt, order=c(1,1,7))

fit2

tsdisplay(residuals(fit2), lag.max=15, main='Seasonal Model Residuals')

fcast <- forecast(fit2, h=30)
plot(fcast)

hold <- window(ts(deseasonal_cnt), start=700)

fit_no_holdout = arima(ts(deseasonal_cnt[-c(700:725)]), order=c(1,1,7))

fcast_no_holdout <- forecast(fit_no_holdout,h=25)
plot(fcast_no_holdout, main=" ")
lines(ts(deseasonal_cnt))

fit_w_seasonality = auto.arima(deseasonal_cnt, seasonal=TRUE)
fit_w_seasonality

seas_fcast <- forecast(fit_w_seasonality, h=30)
plot(seas_fcast)
```
